Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
mini

Reinforcement learning is, on the other hand, typically a model-free approach to control theory.
\footnote{There are, however, approaches to perform model-based reinforcement learning. While we will not focus on these in this paper they are discussed in \cite{tbd1, tbd2}.}
While the model is certainly used to generate training data, it is not directly used by the optimization algorithm.
This provides more flexibility to use model-free RL in instances where the model of the system is not accurately known.
In fact, it has been shown to generally be preferable to use model-free RL in such instances.

@@

>>>>

Reinforcement learning is, on the other hand, typically a model-free approach to control theory.\footnote{There are, however, approaches to perform model-based reinforcement learning. While we will not focus on these in this paper they are discussed in \cite{tbd1, tbd2}.}
While the model is certainly used to generate training data, it is not directly used by the optimization algorithm.
This provides more flexibility to use model-free RL in instances where the model of the system is not accurately known.
In fact, it has been shown to generally be preferable to use model-free RL in such instances.

@@

# Results
